# Setup

```{r}
library(dplyr)
library(stringr)
library(haven)
library(stargazer)

original_data <- read_dta("./cen_ind_2021_pumf_v2.dta")
```

## Data Cleaning

Here we are setting up the data for our Analysis. What we are doing here is filtering out the population we need for our analysis:

-   Agegroup 60 - 64, 65 - 69

-   Remove NA for Labour Force status(lfact) and Immigration Status(immstat)

```{r}
my_data <- original_data %>%
  mutate(across(where(is.labelled), as_factor)) %>%
  filter(agegrp %in% c("60 to 64 years", "65 to 69 years")) %>%
  filter(lfact != "Not available", immstat != "Not applicable")
```

Here we are determining eligible for OAS

-   Person is in labour force if they are either employed or unemployed or 1(employed or self employed)

-   Person is in treatable group age is '65 - 69'

-   Eligible if (immigrant && years_in_canada \>=) 10 or Non-immigrant(Canadian born) We also convert covariates into categorical data

```{r}
my_data <- my_data %>%
  mutate(
    in_labour_force = ifelse(lfact == "1" | grepl("Employed", lfact) | grepl("Unemployed", lfact), 1, 0),
    
    treated_age = ifelse(agegrp == "65 to 69 years", 1, 0),
    
    yrim_numeric = ifelse(immstat == "Immigrants", 
                          as.numeric(as.character(yrim)), 
                          NA),
    
    years_in_can = 2021 - yrim_numeric,
    
    is_eligible = case_when(
      immstat == "Non-immigrants" ~ 1,
      immstat == "Immigrants" & years_in_can >= 10 ~ 1,
      immstat == "Immigrants" & years_in_can < 10  ~ 0,
      TRUE ~ 0
    ),
    
    education   = as.factor(hdgree),
    hh_income   = as.factor(HHInc_AT),  
    gender      = as.factor(Gender),    
    marital     = as.factor(marsth),
    province    = as.factor(pr),
    income      = as.factor(TotInc_AT)
  )
```

## DD Regression

In this our treatment is the is_eligible, if a person is eligible to get treated at go time which in this is at age 65.

$$ 
\begin{align}
  \text{M1}: Y_i &= \beta_0 + \beta_1 \, D_i + \beta_2 \, T_i + \beta_3 \, (D_i \times T_i) +     \varepsilon_i \\
\end{align} 
$$

Cheese

$$
\begin{align}
  \text{Variable meanings} \\ 
  D_i &= \text{Elegibilty for OAS} \\
  T_i &= \text{Go-time 65+}
\end{align}
$$

```{r}
# Simple Regresssion
m1 <- lm(in_labour_force ~ is_eligible + treated_age + is_eligible:treated_age, data = my_data)
# Regression with covariates, no factors
m2 <- lm(in_labour_force ~ is_eligible + treated_age + is_eligible:treated_age + gender , data = my_data)
# Regression with covariates, including factors house hold income and education
m3 <- lm(in_labour_force ~ is_eligible + treated_age + is_eligible:treated_age + gender +
           education + hh_income + marital + province + income, 
         data = my_data)

stargazer(m1, m2, m3, 
          add.lines = list(
        c("Demographic controls", "No", "Yes", "Yes"),
        c("Categorical controls as factors", "No", "No", "Yes")
  ),
          omit = c("education", "hh_income", "marital", "gender", "Constant", "province", "income"),
          omit.stat = c("f", "ser"),
          type = "text")
```

```{r}
table_data <- my_data %>%
  mutate(
    Participation = in_labour_force,
    Age_65_Plus   = treated_age,
    Eligible      = is_eligible,
    Male          = ifelse(as.numeric(Gender) %in% c(2), 1, 0),
    Is_Married    = ifelse(as.numeric(marital) %in% c(2), 1, 0),
    HH_Income     = ifelse(as.numeric(hh_income) > 23, 1, 0),
    Uni_Degree    = ifelse(as.numeric(education) %in% c(9, 10, 11), 1, 0),
    Diploma       = ifelse(as.numeric(education) %in% c(2,3), 1, 0),
    Per_income    = ifelse(income > 90000, 1, 0)
    
  ) %>%
  select(Participation, Age_65_Plus, Eligible, Male, Is_Married, HH_Income, Per_income, Uni_Degree, Diploma, )
stargazer(as.data.frame(table_data), 
          type = "text", 
          title = "Summary for variables of interest",
          digits = 2,
          summary.stat = c("mean", "sd", "min", "max"),
          covariate.labels = c("Labour Force Status", 
                               "Age 65+", 
                               "OAS Eligible",
                               "Gender (Male = 1)", 
                               "Married", 
                               "HH Income",
                               "Per Income",
                               "University Degree",
                               "Diploma"
                           ),
          notes = c("Sample Size of N = 126,446", "Used 90,000 as the middle point for both Income"),
          notes.append = TRUE)
```
